\documentclass[a4paper,10pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{parskip}

% Define colors
\definecolor{darkblue}{RGB}{0, 51, 102}
\definecolor{lightblue}{RGB}{173, 216, 230}
\definecolor{orange}{RGB}{255, 165, 0}

% Title formatting
\titleformat{\section}{\color{darkblue}\large\bfseries}{}{0em}{} % Section formatting
\titleformat{\subsection}{\color{orange}\bfseries}{}{0em}{} % Subsection formatting

\begin{document}

\begin{center}
    {\LARGE \textbf{Your Name}} \\
    \vspace{2mm}
    \faEnvelope \hspace{1mm} \href{mailto:your.email@example.com}{your.email@example.com} \hspace{5mm}
    \faPhone \hspace{1mm} (123) 456-7890 \hspace{5mm}
    \faLinkedin \hspace{1mm} \href{https://www.linkedin.com/in/yourprofile}{yourprofile} \hspace{5mm}
    \faGithub \hspace{1mm} \href{https://github.com/yourprofile}{yourprofile}
\end{center}

\section*{Summary}
Results-driven MLOps Engineer with over 5 years of experience in deploying and managing machine learning models. Proficient in cloud platforms, CI/CD pipelines, and data engineering practices. Passionate about optimizing ML workflows and enhancing model performance.

\section*{Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Programming Languages:} Python, Java, Bash
    \item \textbf{ML Frameworks:} TensorFlow, PyTorch, Scikit-learn
    \item \textbf{Cloud Platforms:} AWS, Azure, GCP
    \item \textbf{Tools:} Docker, Kubernetes, Apache Kafka, MLflow
    \item \textbf{Data Engineering:} SQL, NoSQL, ETL processes
    \item \textbf{CI/CD:} Jenkins, GitHub Actions, Terraform
\end{itemize}

\section*{Experience}

\subsection*{Senior MLOps Engineer}
Company Name, Location \hfill Month Year -- Present
\begin{itemize}[leftmargin=*]
    \item Developed and maintained scalable machine learning pipelines for model training and deployment.
    \item Collaborated with data scientists to integrate ML models into production, enhancing data processing efficiency by 30\%.
    \item Implemented CI/CD practices for ML workflows, reducing deployment time by 40\%.
    \item Monitored model performance and implemented automated alerts for data drift and model decay.
\end{itemize}

\subsection*{MLOps Engineer}
Previous Company Name, Location \hfill Month Year -- Month Year
\begin{itemize}[leftmargin=*]
    \item Designed and deployed cloud infrastructure for machine learning applications on AWS.
    \item Streamlined data ingestion processes, improving data availability for model training.
    \item Worked with cross-functional teams to ensure seamless integration of ML solutions into existing systems.
\end{itemize}

\section*{Education}
\subsection*{Master of Science in Data Science}
University Name, Location \hfill Month Year

\subsection*{Bachelor of Science in Computer Science}
University Name, Location \hfill Month Year

\section*{Certifications}
\begin{itemize}[leftmargin=*]
    \item AWS Certified Machine Learning – Specialty
    \item Google Cloud Professional Data Engineer
\end{itemize}

\end{document}

